---
title: "Final Exam_Rania"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r load libraries, message=FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(tigris)
library(sf)
library(gridExtra)
library(interactions)
```

## Load Data
```{r, message=FALSE}
Main_st_data <- read_csv("finalexam_sampledata.csv")
```

# Question 1

What is the average change in sales for Main street businesses? 
Did sales increase of decrease on average? 
How confident are you about that?

```{r}
t.test(Main_st_data$pct_sales_chng)
```

Mean of x
On average, Main street businesses saw a (2.7%) (increase) in sales. 

95 percent confidence interval:
The 95-percent confidence interval for the (increase) is (2.4 to 3.1) percent. 

p-value
Since the p-value for this estimate is less than (0.001), we can be more than (99.9-percent) confident that sales increased.


## Question 2 

Did the cost of parking change more for some types of businesses than for others?
How confident are you about those differences?

To interpret the regression in a meaningful way, I will first find the most common store type so I can compare other types to it.
```{r}
Main_st_data %>%
  group_by(type) %>%
  summarise(number = n()) %>%
  mutate(percent = round(100*number / sum(number))) %>%
  arrange(desc(number))
```

(Clothing) stores are the most common so I will compare everything back to clothing and relevel the regression back to it

```{r}
Main_st_data <- Main_st_data %>%
  mutate(type = as.factor(type)) %>%
  mutate(type = relevel(type, "Clothing"))
```

I will now do the bivariate regression to see which store types have changes in parking costs comparing to the changes in clothing stores.

```{r}
parking_cost_by_type <- lm(parking_cost_by_type ~ type, data= Main_st_data)
summary(parking_cost_by_type)
```

From the intercept of the regression, the average change in parking costs for clothing stores was an (increase of 11%)
On average, (bookstores) has slightly increased and (drugstores) had slightly decreased but I am less than 95-percent confident that these two differences are significant.

I am at least 95-percent confident that all of the other types had significantly different changes in parking costs than the clothing stores did. 

Parking costs at restaurants increased by about (4) percentage points (more) than at clothing stores. Meaning that parking costs for restaurants increased by 18%.
Parking costs at furniture stores increased by about (7) percentage points (more) than at clothing stores. Meaning that parking costs for furniture stores increased by 4%.
Parking costs at grocery stores increased by about (5) percentage points (less) than at clothing stores.Meaning that parking costs for grocery stores increased by 6%.
Parking costs at gas stations increased by about (10) percentage points (less) than at clothing stores. Meaning that parking costs for gas stations increased by 1%. 


## Question 3 

Not counting any kind of effect of the changes to parking and cycling have had, what kind of 
effect did it have on businesses if the closest transit stop got closer or further away? 


