---
title: "Final Exam_Rania Karamallah"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r load libraries, message=FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(tigris)
library(sf)
library(gridExtra)
library(interactions)
library(ggplot2)
```

## Load Data
```{r, message=FALSE}
Main_st_data <- read_csv("finalexam_sampledata.csv")
```

# Question 1

What is the average change in sales for Main street businesses? 
Did sales increase of decrease on average? 
How confident are you about that?

```{r}
t.test(Main_st_data$pct_sales_chng)
```

Mean of x
On average, Main street businesses saw a (2.7%) (increase) in sales. 

95 percent confidence interval:
The 95-percent confidence interval for the (increase) is (2.4 to 3.1) percent. 

p-value
Since the p-value for this estimate is less than (0.001), I can be more than (99.9-percent) confident that sales increased.


## Question 2 

Did the cost of parking change more for some types of businesses than for others?
How confident are you about those differences?

I will do a bivariate regression to asnwer this questions. To interpret the regression, I will first find the most common store type so I can compare other types to it.
```{r}
Main_st_data %>%
  group_by(type) %>%
  summarise(number = n()) %>%
  mutate(percent = round(100*number / sum(number))) %>%
  arrange(desc(number))
```

(Clothing) stores are the most common so I will compare everything back to clothing and relevel the regression back to it

```{r}
Main_st_data <- Main_st_data %>%
  mutate(type = as.factor(type)) %>%
  mutate(type = relevel(type, "Clothing"))
```

I will now do the bivariate regression to see which store types have changes in parking costs comparing to the changes of parking cost to clothing stores.

```{r}
parking_cost_by_type <- lm(parking_cost_by_type ~ type, data= Main_st_data)


summary(parking_cost_by_type)
```

From the intercept of the regression, the average change in parking costs for clothing stores was an (increase of 11%)
On average, (bookstores) has slightly increased and (drugstores) had slightly decreased but I am less than 95-percent confident that these two differences are significant.

I am at least 95-percent confident that all of the other types had significantly different changes in parking costs than the clothing stores did. 

Parking costs at restaurants increased by about (4) percentage points (more) than at clothing stores. 
Parking costs at furniture stores increased by about (7) percentage points (more) than at clothing stores. 
Parking costs at grocery stores increased by about (5) percentage points (less) than at clothing stores.
Parking costs at gas stations increased by about (10) percentage points (less) than at clothing stores. 


## Question 3 

Not counting any kind of effect of the changes to parking and cycling have had, 
what kind of effect did it have on businesses if the closest transit stop got closer or further away? 

I will run a regression model that will predict the effect on the change in distance to transit on the percent change in sales. I will control for change in parking supply + changes in parking price + changes in bike traffic. 

```{r}
model_1 <- lm(pct_sales_chng ~ transit_dist + parking_cost_change + lost_parking + bike_chng, data = Main_st_data)


summary(model_1)
```


For every one-mile increase in the distance from a transit stop, sales (decrease) by (17-percentage) points, controlling for difference in the changes to parking supply, parking costs, and bike volumes. That is also statistically significant.


## Question 4

Was the effect of transit on sales different for some types of businesses than for others? 
What was the difference, if any? 

I will estimate a regression model with an interaction between transit distance and business type. For consistency with the previous model, I will keep the controls of parking and cycling. I am hypothesizing that distance from a transit stop has an effect on different types of store when considering how much their sales have changed. 

```{r}
model_2 <- lm(pct_sales_chng ~ type + transit_dist + parking_cost_change +lost_parking + bike_chng + 
                type:transit_dist, data = Main_st_data)


summary(model_2)
```

Plot: 
```{r}
interact_plot(model_2, pred = transit_dist, interval = TRUE, modx = type)
```

For gas stations, furniture stores, and grocery stores, the distance to transit did not have a substantial effect on the change in sales. 

For clothing stores, bookstores, drugstores, and restaurants, each additional mile closer to transit was associated with an additional (30-percentage increase) in sales.



